Harris County, Texas residents faced several barriers to voter identification access during the 2016 United States election

### 2024-02-13 paper/paper.qmd
Changed a file path to improve the organization of the GitHub Repository

# Loading the cleaned data
reasons_data_cleaned <- read_csv(here::here("data/replication/reasons_data_cleaned.csv"))

# Loading the Harris County data
reasons_data_harris <- read_csv(here::here("data/replication/reasons_data_harris.csv"))
```

>>>>

# Loading the cleaned data
reasons_data_cleaned <- read_csv(here::here("data/reproduction/reasons_data_cleaned.csv"))

# Loading the Harris County data
reasons_data_harris <- read_csv(here::here("data/reproduction/reasons_data_harris.csv"))
```
